---
title: "Diabete_data_report"
author: "Franklin"
date: "7/26/2017"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse) # utility functions
library(rpart) # for regression trees
library(randomForest) # for random forests
library(modelr)
data = read.csv("./diabetes.csv")
attach(data)
```

## Report

First I want to look at the general summary of the data, so I have a better sense of direction of how to explore the data.

```{r cars}
summary(data)
```

I am going to split data into training set and test set. Then build a model on traning data to test on test data.

```{r pressure}

splitData <- resample_partition(data, c(test = 0.3, train = 0.7))


fit <- rpart(Outcome ~ Pregnancies + Glucose + BloodPressure + SkinThickness
                 + DiabetesPedigreeFunction + Age,control = 6, data = splitData$train)

mae(model = fit, data = splitData$test)

print(head(predict(fit, splitData$test)))

pred_outcome <- predict(fit, splitData$test)

pred_outcome[which(pred_outcome[]>=0.5)] <- 1
pred_outcome[which(pred_outcome[]<=0.5)] <- 0

actual <- as.data.frame(splitData$test)$Outcome

result <- vector("numeric")

for(i in 1 : length(actual)){
  
  result[i]<-pred_outcome[i]==actual[i]
  
}

accuracy <- table(result)

accuracy[2] / (accuracy[1] + accuracy[2] )

target <- "Outcome"
predictors <-  c("Pregnancies","Glucose","BloodPressure","SkinThickness",
                 "Insulin","Age","BMI")

get_mae <- function(maxdepth, target, predictors, training_data, testing_data){
  
  # turn the predictors & target into a formula to pass to rpart()
  predictors <- paste(predictors, collapse="+")
  formula <- as.formula(paste(target,"~",predictors,sep = ""))
  
  # build our model
  model <- rpart(formula, data = training_data,
                 control = rpart.control(maxdepth = maxdepth))
  # get the mae
  pred_outcome <- predict(model, testing_data)

  pred_outcome[which(pred_outcome[]>=0.5)] <- 1
  pred_outcome[which(pred_outcome[]<=0.5)] <- 0
  
  actual <- as.data.frame(testing_data)$Outcome
  
  result <- vector("numeric")

for(i in 1 : length(actual)){
  
  result[i]<-pred_outcome[i]==actual[i]
  
}

accuracy <- table(result)


  return(accuracy[2] / (accuracy[1] + accuracy[2] ))
}

for(i in 1:10){
  mae <- get_mae(maxdepth = i, target = target, predictors = predictors,
                 training_data = splitData$train, testing_data = splitData$test)
  print(glue::glue("Maxdepth: ",i,"\t accuracy: ",mae))
}


```

I changed the number into 1 or 0 if the predicted outcome is higher or lower than 0.5 and check the accuracy. And the accuracy of our model is shown above.

## Plots

Now I want to visually see my data to have a better sense of it.

Frist, I want to see how the variable interact with the outcome.
```{r scatter, echo=TRUE}

ggplot(data = data, aes(x = BMI, y = Outcome)) +
  geom_point()

```
\newline

However, it does not seem to tell me anything. I will try out other variables.

```{r scatter2, echo=TRUE}

ggplot(data = data, aes(x = BMI, y = Age, label = Outcome)) +
  geom_point() +
  geom_smooth(method = "lm") +
      geom_text(check_overlap = T,
              vjust = "bottom", # adjust the vertical orientation
              nudge_y = 1, # move the text up a bit 
              
              size = 4 # make the text smaller (to reduce overlap more)
             ) #



```
\newline


It does not seem to have a strong linear relationship.

##Conclusion

In conclusion, the model I build with the highest accuracy rate is 79.6%. I have not yet plotted the graph of other predictors because I consider unnecessary due few amount of data. However, I have demonstrate my capability of the usings ggplot2 and usage of rpart and randomforest to model my beginner model.

